Appendix for: Deep Reinforcement Learning for Conservation Decisions

### 2021-04-20 manuscript/appendix.Rmd
td3 hyperparameters for cons-v6 (testing :construction:)

noise_std = 0.4805935357322933
action_noise = OrnsteinUhlenbeckActionNoise(mean = np.zeros(1),
                                            sigma = noise_std * np.ones(1))

model = TD3('MlpPolicy', 
            env, 
            verbose = 0, 
            seed = seed,
            "gamma": 0.995,
            "learning_rate":  8.315382409902049e-05,
            "batch_size": 512,
            "buffer_size": 10000,
            "train_freq": 1000,
            "gradient_steps": 1000,
            "n_episodes_rollout": -1,
            "action_noise": action_noise,
            "policy_kwargs": list("net_arch": c(64,64)))

@@

```{r}
model$learn(total_timesteps = 1500000)

>>>>

noise_std = 0.4805935357322933
action_noise = sb3$common$noise$OrnsteinUhlenbeckActionNoise(mean = np$zeros(1L),
                                            sigma = noise_std * np$ones(1L))

model = sb3$TD3('MlpPolicy', 
            env, 
            verbose = 0, 
            seed = seed,
            "gamma"= 0.995,
            "learning_rate"=  8.315382409902049e-05,
            "batch_size"= 512L,
            "buffer_size"= 10000L,
            "train_freq"= 1000L,
            "gradient_steps"= 1000L,
            "n_episodes_rollout"= -1L,
            "action_noise"= action_noise,
            "policy_kwargs"= list("net_arch"= c(64L,64L)))

@@

```{r}
if(!file.exists("cache/td3-conservation.zip")){

  model$learn(total_timesteps=1500000L)
  model$save("cache/td3-conservation")
